%-------------------------
% Resume in Latex
% Credit to Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume,https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
%\usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
 \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Alex Feng} \\ \vspace{1pt}
    \small [REDACTED] $|$ \href{mailto:x@x.com}{\underline{ajfeng@buffalo.edu}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/ajfeng}} $|$
    \href{https://github.com/...}{\underline{github.com/ajfeng4}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University at Buffalo, State University of New York}{Buffalo, NY}
      {Bachelor of Science in Computer Science, Minor in Cybersecurity}{Jan. 2022 -- Dec 2025}
    \resumeSubheading
      {University at Buffalo, State University of New York}{Buffalo, NY}
      {Bachelor of Science in Business Administration}{Jan. 2022 -- Dec 2025}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Web Development Assistant}{Sep 2024 -- Present}
      {University at Buffalo School of Dental Medicine}{Buffalo, NY}
      \resumeItemListStart
        \resumeItem{Redesigned the School of Dental Medicine website using UX best practices, boosting SDM engagement}
        \resumeItem{Resolved over 20 website inconsistencies and bugs, documenting fixes for future reference and improvement}
        \resumeItem{Developed a database suite using Javascript, React, and Python improving data retrieval efficiency}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Undergraduate Teaching and Research Assistant}{Aug. 2024 -- Present}
      {University at Buffalo School of Engineering and Applied Sciences}{Buffalo, NY}
      \resumeItemListStart
        \resumeItem{Research Assistant for Professor Wenyao Xu’s Drink Intake Project responsible for Mobile Development}
        \resumeItem{Built iOS/Android app to improve drinking habits based on detected drinking sounds using React Native.}
        \resumeItem{Assisted Professor Paul Dickson in teaching 3D Game Development using C++ to over 100 students.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineer Intern}{Aug. 2024 -- Dec 2024}
      {Site Software Service Inc}{Jamison, PA}
      \resumeItemListStart
        \resumeItem{Migrated legacy systems to Java and Spring Boot, increasing efficiency  and reducing maintenance costs}
        \resumeItem{Collaborated with cross-functional teams using Git to ensure successful integration, and maintain clean code.}
        \resumeItem{Participated in weekly stand-up meetings and full software development cycles, adhering to Agile methodologies.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineer Intern}{May 2024 -- Aug 2024}
      {Hungie}{New York City, NY}
      \resumeItemListStart
        \resumeItem{{Implemented scalable full-stack features for the MVP app using TypeScript, React Native, Python, and Firebase.}}
        \resumeItem{Reduced technical debt by 50 percent using Tailwind CSS and optimized APIs, improving load time by 20 percent}
        \resumeItem{Integrated alternative APIs and services, reducing costs by 15 percent and updating deprecated systems.}
    \resumeItemListEnd

    \resumeSubheading
      {Director of Procurement}{Aug. 2022 -- Present}
      {Undergraduate Student Association}{Buffalo, NY}
      \resumeItemListStart
        \resumeItem{Negotiated competitive rates with vendors, saving student clubs approximately 10,000 dollars annually.}
        \resumeItem{Managed over 30 weekly purchase orders totaling 5,000 dollars maintaining transparency and accuracy.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd
  


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Drink Intake Tracker} $|$ \emph{Typescript, Python, React Native, PostgreSQL, Supabase, Expo}}{Aug 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a mobile app to track a user's hydration level through vocal recognition}
            \resumeItem{Implemented and designed mobile dashboard and statistics screen to display user hydration}
            \resumeItem{Designed and built database schema, to be used to train the app to recognize when a user is drinking}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Find a Mechanic} $|$ \emph{JavaScript, PHP, React Native, SQL, Expo}}{Sep 2024 -- Dec 2024}
          \resumeItemListStart
            \resumeItem{Built an iOS/Android mobile app connecting users in need of repairs with local garages and mechanics.}
            \resumeItem{Redesigned and modernized the app's UI to streamline the customer to mechanic process using JavaScript}

          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Dystopia} $|$ \emph{JavaScript, CSS, Tailwind, React}}{Jan 2024 -- May 2024}
          \resumeItemListStart
            \resumeItem{Developed a responsive social media application that empowers users to customize their social media landscape.}
            \resumeItem{Used JavaScript and CSS to design and build Dystopia's authentication flow and profile feature}

          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, Typescript, HTML/CSS, Python, Java, PHP, C++, C, SQL, SCSS } \\
     \textbf{Frameworks}{: React.js, React Native, Next.js, Vue.js, Angular,  Node.js, Express.js, Flask, Spring, MaterialUI, Tailwind} \\
     \textbf{Developer Tools}{: Git, GitHub, GitLab, Trello, Jira, Docker, WebStorm, IntelliJ, VSCode, Andriod Studio} \\
     \textbf{Databases}{: Firebase, MongoDB, MySQL, Supabase (Postgre), PHPMyAdmin}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
